Density dependence

### 2020-10-27 analysis/paper/appendix_density_dependence.Rmd
minor formatting changes

We modeled density dependence using a penalized distributed lag non-linear model (DLNM) approach with the `dlnm` package in R [@gasparriniPenalizedFrameworkDistributed2017; @gasparriniDistributedLagLinear2011; @rcoreteamLanguageEnvironmentStatistical2020]. This approach is similar to that of [-@teller2016], in that it makes no assumptions about the shape of the competition kernel. Instead, it fits a two-dimensional spline allowing for a non-linear response to the intensity of conspecific density as well as the distance of conspecifics. We implemented this in a generalized additive model (GAM) framework taking advantage of the penalization features of the `mgcv` package [@woodGeneralizedAdditiveModels2017].

@@

```{r growth-plot, include=TRUE, fig.cap="this is a figure"}
Q_new <- 
  g_growth$model %>% 
  pull(Q) %>%
  as_tibble() %>% 
  summarize(across(everything(), mean)) %>%
  as.matrix()
L_new <- L[1,, drop = FALSE]

@@

fitted <- augment(g_growth, newdata = newdata, se_fit = TRUE, conf.level = 0.95)
ggplot(fitted, aes(x = exp(log_shts), y = exp(.fitted))) +
  geom_jitter(data = ha %>%
                filter(across(shts_0.5_1:shts_4.5_5, ~!is.na(.))),
              aes(x = shts, y = shts_next),
              alpha = 0.2) +
  geom_line(color = "blue") +
  geom_ribbon(aes(ymin = exp(.fitted - .se.fit*1.96), ymax = exp(.fitted + .se.fit*1.96)), alpha = 0.4) +
  labs(x = "#shoots (t)", y = "#shoots (t + 1)") +
  theme_bw()
```

@@

```{r}
pred_growth <- cb_margeff(Q, L, g_growth)
```

@@

Plant size had a significant, nearly quadratic (on a logit scale), effect on survival in continuous forest ($\chi^2$ = 112.2, edf = 2.1, P \< 0.001), but a linear (on a logit scale) effect in 1 ha fragments ($\chi^2$ = 15.63, edf = 1, P \< 0.001) (Figure \@ref(fig:surv-plot)). However, there were no significant effects of habitat ($\chi^2$ = 0.002, df = 1, P = 0.964) or conspecific density ($\chi^2$ = 5.326, edf = 2, P = 0.0699) on survival.

>>>>

We modeled density dependence using a penalized distributed lag non-linear model (DLNM) approach with the `dlnm` package in R [@gasparriniPenalizedFrameworkDistributed2017; @gasparriniDistributedLagLinear2011; @rcoreteamLanguageEnvironmentStatistical2020]. This approach is similar to that of Teller et al. [-@teller2016], in that it makes no assumptions about the shape of the competition kernel. Instead, it fits a two-dimensional spline allowing for a non-linear response to the intensity of conspecific density as well as the distance of conspecifics. We implemented this in a generalized additive model (GAM) framework taking advantage of the penalization features of the `mgcv` package [@woodGeneralizedAdditiveModels2017].

@@

```{r growth-plot, include=TRUE, fig.cap="this is a figure"}
Q_new <- 
  g_growth_scat$model %>% 
  pull(Q) %>%
  as_tibble() %>% 
  summarize(across(everything(), mean)) %>%
  as.matrix()
L_new <- L[1,, drop = FALSE]

@@

fitted <-
  augment(
    g_growth_scat,
    newdata = newdata,
    se_fit = TRUE,
    conf.level = 0.95
  )
ggplot(fitted, aes(x = exp(log_shts), y = exp(.fitted))) +
  geom_jitter(data = ha %>%
                filter(across(shts_0.5_1:shts_4.5_5, ~!is.na(.))),
              aes(x = shts, y = shts_next),
              alpha = 0.2) +
  geom_line(color = "blue") +
  geom_ribbon(aes(ymin = exp(.fitted - .se.fit*1.96), ymax = exp(.fitted + .se.fit*1.96)), alpha = 0.4) +
  labs(x = "#shoots (t)", y = "#shoots (t + 1)") +
  theme_bw()
```

@@

```{r}
pred_growth <- cb_margeff(Q, L, g_growth_scat)
```

@@

Plant size had a significant, nearly quadratic (on a logit scale), effect on survival in continuous forest ($\chi^2$ = 112.2, edf = 2.1, P \< 0.001), but a linear (on a logit scale) effect in 1 ha fragments ($\chi^2$ = 15.63, edf = 1, P \< 0.001), but their 95% confidence intervals overlap (Figure \@ref(fig:surv-plot)). However, there were no significant effects of habitat ($\chi^2$ = 0.002, df = 1, P = 0.964) or conspecific density ($\chi^2$ = 5.326, edf = 2, P = 0.0699) on survival.
